### 2016-03-08 paper/algorithm.tex
yasu

\section{Swarm Fusion Method}

Swarm Fusion is a natural multi-core extension of Fusion Move
Method. Take a multi-threading environment to explain our idea, which is
also applicable to other parallel computation environments such as cloud
computing. Every thread $T_i$ keeps track of a solution $S_i$, and
repeats updating $S_i$ by fusion ($i = 1, 2, \cdots N$). Two parameters
$\alpha_i$ and $\beta_i$ control the behavior of fusion steps in each
thread $T_i$. $\alpha_i$ specifies how many solution proposals are to be
generated from proposal generation schemes. Similarly, $\beta_i$
specifies how many solutions in the other threads are to be
fused. Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
configuration, the first thread $T_1$ fuses its current solution $S_1$,
two new proposal solutions (e.g., by randomly picking two proposal
generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
other three threads. This is a multi-way fusion with a non-submodular
energy in general, and message passing algorithm such as
TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
another.

Our model is flexible. For example, a parallel fusion move algorithm by
Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_$

>>>>

\section{Swarm Fusion Method}
\yasu{need to polish, reads very bad.}  Swarm Fusion is a natural
multi-core extension of Fusion Move Method. Take a multi-threading
environment to explain our idea, which is also applicable to other
parallel computation environments such as cloud computing. Assume we
have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$. There are two places to
collect solutions or solution proposals for fusion. First, the {\it
proposal generation pool} can generate new solution proposals on
request. Second, the {\it solution pool} stores the fused solutions from
all the threads. At default, each thread keeps a single current solution
in the pool, but the scheme can be more general.  Two parameters
$\alpha_i$ and $\beta_i$ control the behavior of each fusion step in
$T_i$. The thread collects $\alpha_i$ solution proposals and $\beta_i$
solutions from the pool

$\alpha_i$ specifies how many solution proposals are generated
from proposal generation schemes for a fusion step. Similarly, $\beta_i$
specifies how many current solutions in the other threads are to be
fused. Furthermore, one can control how to pick proposal generation
schemes and how to choose other threads for using the current solutions
(e.g., random or certain algorithm).

Our framework is general, and many existing parallel fusion algorithms
are just special cases of our framework.
%
For example, the parallel fusion algorithm by Lempitsky et
al.~\cite{viktor} always performs binary fusion between the current
solution and another label, which can be achieved by setting $\alpha_i =
1$ and $\beta_i = 0$ for all the threads. The algorithm by
Veksler~\cite{olga} or Dejong et al.~\cite{dejong} are a little complex,
as they need to store as many intermediate solutions as labels, which is
more than the number of threads. Our framework keeps one solution in
each thread, but

lets each thread keep a
single solution, but

Also note that these existing algorithms seek to parallelize
alpha-expansion with constant solution proposals, and are not true
fusion move algorithms.

hierarchically fuses all the
labels. Depending on the input {\it tree structure}, every thread might
fuse different numbers of existing solutions

We now illustrate the power of Swarm Fusion framework for three problems
in Computer Vision.

Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
configuration, the first thread $T_1$ fuses its current solution $S_1$,
two new proposal solutions (e.g., by randomly picking two proposal
generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
other three threads. This is a multi-way fusion with a non-submodular
energy in general, and message passing algorithm such as
TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
another.

Our model is flexible. For example, a parallel fusion move algorithm by
Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$

### 2016-03-08 paper/introduction.tex
yasu

Our approach is extremely simple in concept, and will instantly benefit
every Computer Vision researcher or engineer, who currently uses fusion
move algorithm to solve challenging problems. We will share our
implementation of the algorithm. The rest of the paper is organized as
follows. Section~\ref{section:related_work}....

>>>>

We have validated our ideas on three problems in Computer Vision,
stereo, optical flow, and layered depthmap estimation. \yasu{add more
once we see results.}  Our approach is extremely simple in concept, and
will instantly benefit every Computer Vision researcher or engineer, who
currently uses fusion move algorithm to solve challenging problems. We
will share our implementation of the algorithm. The rest of the paper is
organized as follows. Section~\ref{section:related_work}....
